### 2025-05-20 SuppSections.Rmd
Added empty stomach sample size.

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
aps1 <- AP_stos %>% filter(length > 29)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)

acs0 <- AC_stos %>% filter(length < 18)
aps0 <- AP_stos %>% filter(length < 30)
ghs0 <- GH_stos %>% filter(length < 20)

# table(acs0$pa, acs0$year)
# table(acs1$pa, acs1$year)
# table(acs2$pa, acs2$year)
# table(aps0$pa, aps0$year)
# table(aps1$pa, aps1$year)
# table(ghs0$pa, ghs0$year)
# table(ghs1$pa, ghs1$year)
# table(ghs2$pa, ghs2$year)

Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1995)
Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
Eaps1 <- AP_stos %>% filter(length > 29)
Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
Eghs2 <- GH_stos %>% filter(length > 40)

Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)
Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)

@@

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
apf1 <- AP_stof %>% filter(length > 29)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)

acf0 <- AC_stof %>% filter(length < 18)
apf0 <- AP_stof %>% filter(length < 30)
ghf0 <- GH_stof %>% filter(length < 20)

# table(acf0$pa, acf0$year)
# table(acf1$pa, acf1$year)
# table(acf2$pa, acf2$year)
# table(apf0$pa, apf0$year)
# table(apf1$pa, apf1$year)
# table(ghf0$pa, ghf0$year)
# table(ghf1$pa, ghf1$year)
# table(ghf2$pa, ghf2$year)

Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
Eapf1 <- AP_stof %>% filter(length > 29)
Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Eghf2 <- GH_stof %>% filter(length > 40)

Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1982 & year == 1983 & year == 1988)
Eapf0 <- AP_stof %>% filter(length < 30)
Eghf0 <- GH_stof %>% filter(length < 20)

@@

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
aps1 <- AP_stos %>% filter(length > 29)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)

acs0 <- AC_stos %>% filter(length < 18)
aps0 <- AP_stos %>% filter(length < 30)
ghs0 <- GH_stos %>% filter(length < 20)

# table(acs0$pa, acs0$year)
# table(acs1$pa, acs1$year)
# table(acs2$pa, acs2$year)
# table(aps0$pa, aps0$year)
# table(aps1$pa, aps1$year)
# table(ghs0$pa, ghs0$year)
# table(ghs1$pa, ghs1$year)
# table(ghs2$pa, ghs2$year)

Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1998 & year != 2017)
Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)
Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
Cghs2 <- GH_stos %>% filter(length > 40)

Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)
Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)

@@

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
apf1 <- AP_stof %>% filter(length > 29)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)

acf0 <- AC_stof %>% filter(length < 18)
apf0 <- AP_stof %>% filter(length < 30)
ghf0 <- GH_stof %>% filter(length < 20)

# table(acf0$pa, acf0$year)
# table(acf1$pa, acf1$year)
# table(acf2$pa, acf2$year)
# table(apf0$pa, apf0$year)
# table(apf1$pa, apf1$year)
# table(ghf0$pa, ghf0$year)
# table(ghf1$pa, ghf1$year)
# table(ghf2$pa, ghf2$year)

Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)
Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Cghf2 <- GH_stof %>% filter(length > 40)

Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)
Cghf0 <- GH_stof %>% filter(length < 20)

@@

                 ac0_fall = c(rep(0,11), dfac0$ac0_fall[1:16], 0, dfac0$ac0_fall[17:24], rep(0,1)),
                 ac1_fall = c(dfac1$ac1_fall),
                 ac2_fall = c(dfac2$ac2_fall[1:11], 0, dfac2$ac2_fall[12:36]))
write.csv(ac, file = "./Extra/acseason.csv")

@@

  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,

@@

@@

  C.pempty =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,

@@

                nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100)

@@

sample_size <- sample_size %>% mutate(E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))

write.csv(x = sample_size, file = "./Extra/samplesize.csv")

>>>>

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)
aps1 <- AP_stos %>% filter(length > 29)

acs0 <- AC_stos %>% filter(length < 18)
ghs0 <- GH_stos %>% filter(length < 20)
aps0 <- AP_stos %>% filter(length < 30)

table(acs0$pa, acs0$year)
table(acs1$pa, acs1$year)
table(acs2$pa, acs2$year)
table(ghs0$pa, ghs0$year)
table(ghs1$pa, ghs1$year)
table(ghs2$pa, ghs2$year)
table(aps0$pa, aps0$year)
table(aps1$pa, aps1$year)

Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1995)
Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
Eghs2 <- GH_stos %>% filter(length > 40)
Eaps1 <- AP_stos %>% filter(length > 29)

Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)
Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)

@@

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)
apf1 <- AP_stof %>% filter(length > 29)

acf0 <- AC_stof %>% filter(length < 18)
ghf0 <- GH_stof %>% filter(length < 20)
apf0 <- AP_stof %>% filter(length < 30)

table(acf0$pa, acf0$year)
table(acf1$pa, acf1$year)
table(acf2$pa, acf2$year)
table(apf0$pa, apf0$year)
table(apf1$pa, apf1$year)
table(ghf0$pa, ghf0$year)
table(ghf1$pa, ghf1$year)
table(ghf2$pa, ghf2$year)

Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Eghf2 <- GH_stof %>% filter(length > 40)
Eapf1 <- AP_stof %>% filter(length > 29)

Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1988)
Eghf0 <- GH_stof %>% filter(length < 20)
Eapf0 <- AP_stof %>% filter(length < 30)

@@

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)
aps1 <- AP_stos %>% filter(length > 29)

acs0 <- AC_stos %>% filter(length < 18)
ghs0 <- GH_stos %>% filter(length < 20)
aps0 <- AP_stos %>% filter(length < 30)

table(acs0$pa, acs0$year)
table(acs1$pa, acs1$year)
table(acs2$pa, acs2$year)
table(ghs0$pa, ghs0$year)
table(ghs1$pa, ghs1$year)
table(ghs2$pa, ghs2$year)
table(aps0$pa, aps0$year)
table(aps1$pa, aps1$year)

Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1998 & year != 2017)
Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
Cghs2 <- GH_stos %>% filter(length > 40)
Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)

Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)
Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)

@@

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)
apf1 <- AP_stof %>% filter(length > 29)

acf0 <- AC_stof %>% filter(length < 18)
ghf0 <- GH_stof %>% filter(length < 20)
apf0 <- AP_stof %>% filter(length < 30)

table(acf0$pa, acf0$year)
table(acf1$pa, acf1$year)
table(acf2$pa, acf2$year)
table(apf0$pa, apf0$year)
table(apf1$pa, apf1$year)
table(ghf0$pa, ghf0$year)
table(ghf1$pa, ghf1$year)
table(ghf2$pa, ghf2$year)

Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Cghf2 <- GH_stof %>% filter(length > 40)
Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)

Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
Cghf0 <- GH_stof %>% filter(length < 20)
Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)

@@

                 ac0_fall = c(rep(0,4), dfac0$ac0_fall[1], rep(0,6), dfac0$ac0_fall[1:16], 0, dfac0$ac0_fall[17:24], rep(0,1)),
                 ac1_fall = c(dfac1$ac1_fall),
                 ac2_fall = c(dfac2$ac2_fall[1:11], 0, dfac2$ac2_fall[12:36]))
write.csv(ac, file = "./Extra/acseason.csv")

@@

  E.pcapelin =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,

@@

  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & empty == TRUE))/nrow(filter(Tac0, geartype == "engel"))*100,
                nrow(filter(Tac1, geartype == "engel" & empty == TRUE))/nrow(filter(Tac1, geartype == "engel"))*100,
                nrow(filter(Tac2, geartype == "engel" & empty == TRUE))/nrow(filter(Tac2, geartype == "engel"))*100,
                nrow(filter(Tgh0, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh0, geartype == "engel"))*100,
                nrow(filter(Tgh1, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh1, geartype == "engel"))*100,
                nrow(filter(Tgh2, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh2, geartype == "engel"))*100,
                nrow(filter(Tap0, geartype == "engel" & empty == TRUE))/nrow(filter(Tap0, geartype == "engel"))*100,
                nrow(filter(Tap1, geartype == "engel" & empty == TRUE))/nrow(filter(Tap1, geartype == "engel"))*100),

@@

  C.pcapelin =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,

@@

                  nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100),
  C.pempty = c(nrow(filter(Tac0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac0, geartype == "campelen"))*100,
                nrow(filter(Tac1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac1, geartype == "campelen"))*100,
                nrow(filter(Tac2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac2, geartype == "campelen"))*100,
                nrow(filter(Tgh0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh0, geartype == "campelen"))*100,
                nrow(filter(Tgh1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh1, geartype == "campelen"))*100,
                nrow(filter(Tgh2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh2, geartype == "campelen"))*100,
                nrow(filter(Tap0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap0, geartype == "campelen"))*100,
                nrow(filter(Tap1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap1, geartype == "campelen"))*100)

@@

sample_size <- sample_size %>% mutate(E.pcapelin = format(E.pcapelin, digits = 4), C.pcapelin = format(C.pcapelin, digits = 4),
                                      E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))

write.csv(x = sample_size, file = "./Extra/samplesize_16.05.25.csv")
